\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{bm}

\title{Triadic Dynamics on a Toroidal Harmonic Bundle:\\
\large $\varphi$-Scaled Resonances, Limit-Cycle Attractors, and a Hyperdimensional Encoding}
\author{Darryl C. Novotny \and Collaborators}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
We present a tractable framework in which (i) dynamics evolve on a torus fibered by scale, (ii) interactions are tri-linear (triadic closure), (iii) a golden-ratio ladder organizes resonances and retuning, and (iv) macroscopic limit cycles arise in hypergraph-coupled oscillators. We provide operational proxies for geometric ``tension,'' derive $\varphi$-robustness via KAM-style conditions, and show that retuning has predictable latency with ladder distance. A methods pipeline---bispectrum/bicoherence, diffusion-map torus recovery, Koopman spectra, and hyperdimensional encodings---yields falsifiable predictions and cross-platform comparability (optics, superconducting circuits, classical oscillator networks, and neural signals). Open-source code accompanies this manuscript.
\end{abstract}

\section{Introduction}
Motivation; related work on three-wave mixing, quasi-periodicity and tori; our contributions.

\section{Geometry and the $\varphi$-Ladder}
Let $S^3\\subset\\mathbb{R}^4$. The Clifford torus embedding is
\[
\\iota(u,v)=\\tfrac{1}{\\sqrt{2}}(\\cos u,\\sin u,\\cos v,\\sin v).
\]
Define a bundle $\\pi:\\mathcal{B}\\to\\mathbb{R}$ with fiber $\\pi^{-1}(s)\\cong \\mathbb{T}^2$ and $s=\\log f$. The golden-ratio ladder obeys $s_{k+1}=s_k+\\log\\varphi$. We define a scale-dependent metric $g_s$ and a proxy tension functional $\\mathcal{T}(s)=\\lVert\\mathrm{II}_s\\rVert_{g_s}$.

\section{Tri-Linear Closure and Resonance Web}
Triad Hamiltonian for modes $a,b,c$:
\[
H=\\sum_m \\omega_m(s) a_m^\\* a_m + \\kappa(s)(a b c + a^\\* b^\\* c^\\*).
\]
Near-resonance selection rule $|\\pm\\omega_a\\pm\\omega_b\\pm\\omega_c|<\\epsilon$. Robustness of invariant tori follows from Diophantine/KAM conditions; $\varphi$ gives maximal persistence.

\section{Retuning as Heteroclinic Motion}
We model retuning as transitions along stable/unstable manifolds between invariant tori indexed by ladder step $k$. Latency scales with $|\\Delta s|=|\\Delta k|\\log\\varphi$.

\section{Hypergraph Limit-Cycle Model}
Stuart--Landau nodes with triadic edges:
\[
\\dot{z}_i=(\\alpha-|z_i|^2)z_i + \\sum_{(i,j,k)} J_{ijk} z_j z_k + \\eta_i.
\]
Order parameters: pairwise $R_2$ and triadic $R_3=\\langle e^{i(\\phi_i+\\phi_j+\\phi_k)}\\rangle$. Koopman spectra (EDMD) identify dominant limit cycles.

\section{Methods and Measurements}
Bispectrum/bicoherence; diffusion-map torus recovery; persistent homology; EDMD. Simulation protocols and datasets.

\section{Hyperdimensional Encoding}
Vectors for scales $\\mathbf{F}_k$, modes $\\mathbf{A}_i$, geometry $\\mathbf{T}$; triad binding and slice codes yield state vectors enabling retrieval and causal probing.

\section{Predictions \& Experiments}
(1) $\\varphi$-robustness vs. rationals (KAM plateau width); (2) rigid, narrow bicoherence islands at ladder indices; (3) retuning latency $\~\\,|\\Delta k|$.

\section{Discussion and Limitations}
Scope; modular biological hypotheses; future work (bundle connections, Spin(8) triality).

\\paragraph{Code:} \\url{https://example.com} (replace with repo URL).

\\end{document}
